Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-19 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add code to load grid library

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(hurricaneexposure)
# install hurricane exposure data package if you don't already have it
# library(devtools)
# install_github("geanders/hurricaneexposuredata")
library(hurricaneexposuredata)
library(knitr)
library(ggplot2)
library(gridExtra)
library(plyr)
library(dplyr)
library(tidyr)
library(choroplethr)
library(RColorBrewer)
```

>>>>

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(hurricaneexposure)
# install hurricane exposure data package if you don't already have it
# library(devtools)
# install_github("geanders/hurricaneexposuredata")
library(hurricaneexposuredata)
library(knitr)
library(ggplot2)
library(grid)
library(gridExtra)
library(plyr)
library(dplyr)
library(tidyr)
library(choroplethr)
library(RColorBrewer)
```
